### 2016-09-01 FrontBackmatter/Introduction.tex
Switch to glossaries package for acronyms

Faced with the problem of describing such a diverse array of effects,
two main models have emerged in the past decades, each with its
strengths and weaknesses.
Both can be classified as \emph{multiscale} (or \emph{focused})
models~\autocite{Nobel2013} and hinge on the same idea: treat different
parts of the system with different methods and couple these methods by
bridging "scales" at the boundary, \emph{vide infra}.
While both models treat the molecular degrees of freedom at the quantum
mechanical level, their approach to the microscopic description of the
degrees of freedom of the environment differs:
\begin{itemize}
 \item
   \emph{Discrete} (or \emph{explicit}) models explicitly treat those
   degrees of freedom.
   This is either achieved by a cheaper quantum mechanical
   method~\autocite{Vreven2006-gx} or by \ac{MM}.~\autocite{Senn2009-sk}
   In the latter approach, commonly dubbed \acs{QM}/\acs{MM}, the \acs{MM}
   region can either be polarizable~\autocite{MMPol} or non
   polarizable.~\autocite{MM}
 \item
   \emph{Continuum} (or \emph{implicit}) completely remove the degrees
   of freedom of the environment from the picture, replacing it with a
   structureless continuum.
   The effect of this continuum is described, classically, \emph{via}
   its bulk properties.~\autocite{Onsager1936-wf, Miertus1981-mm}
\end{itemize}
\acs{QM}/\acs{MM} models can capture, albeit approximately, the effect
of the atomistic nature of the environment on the active part of the
system.
However, they demand a statistical average of environment configurations
to yield results of any significance. Moreover, a large number
\emph{cutoff} for the \acs{MM} region is usually required to converge
long-range electrostatic interactions.~\autocite{Something here??}
Continuum models avoid both problems at once. Statistical averaging is
built into the model \emph{via} their parametrization by
means of the environment's bulk properties, such as the permittivity.
In addition, long-range electrostatics is treated exactly.
Unfortunately, atomistic detail is lost and it is then impossible to
recover a satisfactory description of specific effects.
To partly alleviate these sources of error, the \acs{QM}/\acs{MM} and
\acs{QM}/Continuum methods can and have been successfully combined to
yield the three-layer \acs{QM}/\acs{MM}/Continuum method.~\autocite{Curutchet, Steindal Lipparini}
Figure \ref{fig:qm-to-multiscale} schematically portrays the transition
from a full \acs{QM} model of the relevant system to its multiscale
representations.

@@

Chapter \ref{ch:CSM} will present an overview of the \ac{PCM} for
solvation.
I will present a nontechnical discussion of the mathematical details of
the model and an outline of current methodologies for the solution of
the associated governing equations.
Borrowing from the work of \citeauthor{Lipparini2010-be},\autocite{Lipparini2010-be,
Lipparini2015-lq} I will introduce a unifying theoretical formalism for
\acs{QM}/Continuum, \acs{QM}/\acs{MM} and \acs{QM}/\acs{MM}/Continuum models that will
be extensively used throughout the thesis.

>>>>

Faced with the problem of describing such a diverse array of effects,
two main models have emerged in the past decades, each with its
strengths and weaknesses.
Both can be classified as \emph{multiscale} (or \emph{focused})
models~\autocite{Nobel2013} and hinge on the same idea: treat different
parts of the system with different methods and couple these methods by
bridging "scales" at the boundary, \emph{vide infra}.
While both models treat the molecular degrees of freedom at the quantum
mechanical level, their approach to the microscopic description of the
degrees of freedom of the environment differs:
\begin{itemize}
 \item
   \emph{Discrete} (or \emph{explicit}) models explicitly treat those
   degrees of freedom.
   This is either achieved by a cheaper quantum mechanical
   method~\autocite{Vreven2006-gx} or by \gls{MM}.~\autocite{Senn2009-sk}
   In the latter approach, commonly dubbed \acrshort{QM}/\acrshort{MM}, the \acrshort{MM}
   region can either be polarizable~\autocite{MMPol} or non
   polarizable.~\autocite{MM}
 \item
   \emph{Continuum} (or \emph{implicit}) completely remove the degrees
   of freedom of the environment from the picture, replacing it with a
   structureless continuum.
   The effect of this continuum is described, classically, \emph{via}
   its bulk properties.~\autocite{Onsager1936-wf, Miertus1981-mm}
\end{itemize}
\acrshort{QM}/\acrshort{MM} models can capture, albeit approximately, the effect
of the atomistic nature of the environment on the active part of the
system.
However, they demand a statistical average of environment configurations
to yield results of any significance. Moreover, a large number
\emph{cutoff} for the \acrshort{MM} region is usually required to converge
long-range electrostatic interactions.~\autocite{Something here??}
Continuum models avoid both problems at once. Statistical averaging is
built into the model \emph{via} their parametrization by
means of the environment's bulk properties, such as the permittivity.
In addition, long-range electrostatics is treated exactly.
Unfortunately, atomistic detail is lost and it is then impossible to
recover a satisfactory description of specific effects.
To partly alleviate these sources of error, the \acrshort{QM}/\acrshort{MM} and
\acrshort{QM}/Continuum methods can and have been successfully combined to
yield the three-layer \acrshort{QM}/\acrshort{MM}/Continuum method.~\autocite{Curutchet, Steindal Lipparini}
Figure \ref{fig:qm-to-multiscale} schematically portrays the transition
from a full \acrshort{QM} model of the relevant system to its multiscale
representations.

@@

Chapter \ref{ch:CSM} will present an overview of the \gls{PCM} for
solvation.
I will present a nontechnical discussion of the mathematical details of
the model and an outline of current methodologies for the solution of
the associated governing equations.
Borrowing from the work of \citeauthor{Lipparini2010-be},\autocite{Lipparini2010-be,
Lipparini2015-lq} I will introduce a unifying theoretical formalism for
\acrshort{QM}/Continuum, \acrshort{QM}/\acrshort{MM} and \acrshort{QM}/\acrshort{MM}/Continuum models that will
be extensively used throughout the thesis.

### 2016-09-01 FrontBackmatter/Notation.tex
Appearance of notation should be fixed
Switch to glossaries package for acronyms

@@

\renewcommand{\nomname}{
Notations, Conventions and Units
}
\renewcommand{\nompreamble}{
A number of notations and typographic conventions has been adopted in
order to maintain consistency throughout. We summarize them here.
Hartree atomic units are used throughout:~\autocite{Whiffen1978-xx, Mohr2012-zc}
\begin{equation*}
  \si{\electronmass} = \si{\elementarycharge} = \hslash = 4\pi\diel_0 = 1
\end{equation*}
the unit of length is the Bohr \si{\bohr}, while that of energy is the Hartree \si{\hartree}.
The speed of light is then:
\begin{equation*}
  c = \SI{137.035999074}{\bohr\hartree\per\planckbar}
\end{equation*}
}

% Basic Notation
\nomenclature[A, 01]{$u_E$}{Restriction (trace) of the function $u$ to the set $E$}
\nomenclature[A, 02]{$\Span{\vect{v}_1, \ldots, \vect{v}_n}$}{Vector space spanned by the vectors $\vect{v}_1, \ldots, \vect{v}_n$}
\nomenclature[A, 03]{$\delta_{ij}$}{Kronecker symbol: $\delta_{ij}=1i$ if $i=j$ and 0 otherwise}
% Vectors and Matrices
\nomenclature[B, 01]{$\vect{v}, \vect{q}$}{Vectors}
\nomenclature[B, 02]{$\mat{K}, \mat{F}$}{Matrices}
\nomenclature[B, 03]{$\mathbb{R}^{m, n}$}{Vector space of real-valued $m\times n$ matrices}
\nomenclature[B, 04]{$\Tr\mat{A}$}{Trace of $\mat{A}$. For $\mat{A}\in\mathbb{R}^{n, n}$, $\Tr\mat{A}=\sum_{i=1}^n A_{ii}$}
\nomenclature[B, 05]{$0_N, I_N$}{The zero and the identity in an $N$-dimensional vector space}
% Operators
\nomenclature[C, 01]{$\bi{A}, \bi{D}$}{Integral operators}
\nomenclature[C, 02]{$H, \varPhi$}{First or second quantized $N$-electron operators}
% Function Spaces
\nomenclature[D, 01]{$\norm{u}{X}$}{Norm of $u$ in the normed space $X$}
\nomenclature[D, 02]{$\mathcal{C}^0(\Omega)$}{Space of continuous functions on $\Omega\subset\mathbb{R}^d$}
\nomenclature[D, 03]{$\mathcal{C}^k(\Omega)$}{Space of $k$ times continuously differentiable functions on $\Omega$}
\nomenclature[D, 04]{$L^p(\Omega)$}{Space of functions whose $p$-th power is Lebesgue integrable on $\Omega$}
\nomenclature[D, 05]{$\norm{u}{0, p, \Omega}$}{Norm in $L^p(\Omega)$: $\norm{u}{0, p, \Omega} = (\int_\Omega\diff\vect{r} |u(\vect{r})|^p)^\frac{1}{p}$}
\nomenclature[D, 06]{$\norm{u}{\Omega}$}{Norm in $L^2(\Omega)$: $\norm{u}{\Omega} = \norm{u}{0, 2,\Omega} = \sqrt{\int_\Omega\diff\vect{r} |u(\vect{r})|^2}$}
\nomenclature[D, 07]{$H^s(\Omega)$}{Sobolev space of order $s$ of functions whose derivative up to order $s$ are in $L^2(\Omega)$}
\nomenclature[D, 08]{$H_0^s(\Omega)$}{Space of functions in $H^2(\Omega)$ with null trace on the boundary of $\Omega$}
\nomenclature[D, 09]{$|u|_{s, \Omega}$}{Seminorm in $H^s(\Omega)$: $|u|_{s, \Omega} \coloneq \sum_{|\alpha|=s}\norm{\partial^\alpha u}{\Omega}$}
\nomenclature[D, 10]{$\norm{u}{s, \Omega}$}{Norm in $H^s(\Omega)$: $\norm{u}{s, \Omega} \coloneq \sum_{l \leq s} |u|_{l, \Omega}$}
% Molecular Quantum Mechanics
\nomenclature[E, 01]{$r, s, t$}{General \acl{MO} indices}
\nomenclature[E, 02]{$i, j, k$}{Occupied \acl{MO} indices}
\nomenclature[E, 03]{$a, b, c$}{Virtual \acl{MO} indices}
\nomenclature[E, 04]{$\kappa, \lambda, \mu$}{One-electron basis functions indices}

>>>>

%\chapter*{Notations, conventions and units}
\addcontentsline{toc}{chapter}{\tocEntry{Notations, conventions and units}}

@@

\renewcommand{\nomname}{
Notations, Conventions and Units
}

\renewcommand{\nompreamble}{
A number of notations and typographic conventions has been adopted in
order to maintain consistency throughout. We summarize them here.
Hartree atomic units are used throughout:~\autocite{Whiffen1978-xx, Mohr2012-zc}
\begin{equation*}
  \si{\electronmass} = \si{\elementarycharge} = \hslash = 4\pi\diel_0 = 1
\end{equation*}
the unit of length is the Bohr \si{\bohr}, while that of energy is the Hartree \si{\hartree}.
The speed of light is then:
\begin{equation*}
  c = \SI{137.035999074}{\bohr\hartree\per\planckbar}
\end{equation*}
}

% Basic Notation
\nomenclature[A, 01]{$u_E$}{Restriction (trace) of the function $u$ to the set $E$}
\nomenclature[A, 02]{$\Span{\vect{v}_1, \ldots, \vect{v}_n}$}{Vector space spanned by the vectors $\vect{v}_1, \ldots, \vect{v}_n$}
\nomenclature[A, 03]{$\delta_{ij}$}{Kronecker symbol: $\delta_{ij}=1i$ if $i=j$ and 0 otherwise}
\nomenclature[A, 04]{$\scalprod[X]{u}{v}$}{Scalar product of $u$ and $v$ in the Hilbert space $X$}
\nomenclature[A, 05]{$\norm{u}{X}$}{Norm of $u$ in the normed space $X$}
% Vectors and Matrices
\nomenclature[B, 01]{$\vect{v}, \vect{q}$}{Vectors}
\nomenclature[B, 02]{$\mat{K}, \mat{F}$}{Matrices}
\nomenclature[B, 03]{$\mathbb{R}^{m, n}$}{Vector space of real-valued $m\times n$ matrices}
\nomenclature[B, 04]{$\Tr\mat{A}$}{Trace of $\mat{A}$. For $\mat{A}\in\mathbb{R}^{n, n}$, $\Tr\mat{A}=\sum_{i=1}^n A_{ii}$}
\nomenclature[B, 05]{$0_N, I_N$}{The zero and the identity in an $N$-dimensional vector space}
% Operators
\nomenclature[C, 01]{$\bi{A}, \bi{D}$}{Integral operators}
\nomenclature[C, 02]{$H, \varPhi$}{First or second quantized $N$-electron operators}
% Function Spaces
\nomenclature[D, 02]{$\mathcal{C}^0(\Omega)$}{Space of continuous functions on $\Omega\subset\mathbb{R}^d$}
\nomenclature[D, 03]{$\mathcal{C}^k(\Omega)$}{Space of $k$ times continuously differentiable functions on $\Omega$}
\nomenclature[D, 04]{$L^p(\Omega)$}{Space of functions whose $p$-th power is Lebesgue integrable on $\Omega$}
\nomenclature[D, 05]{$\norm{u}{0, p, \Omega}$}{Norm in $L^p(\Omega)$: $\norm{u}{0, p, \Omega} = (\int_\Omega\diff\vect{r} |u(\vect{r})|^p)^\frac{1}{p}$}
\nomenclature[D, 06]{$\norm{u}{\Omega}$}{Norm in $L^2(\Omega)$: $\norm{u}{\Omega} = \norm{u}{0, 2,\Omega} = \sqrt{\int_\Omega\diff\vect{r} |u(\vect{r})|^2}$}
\nomenclature[D, 07]{$H^s(\Omega)$}{Sobolev space of order $s$ of functions whose derivative up to order $s$ are in $L^2(\Omega)$}
\nomenclature[D, 08]{$H_0^s(\Omega)$}{Space of functions in $H^2(\Omega)$ with null trace on the boundary of $\Omega$}
\nomenclature[D, 09]{$|u|_{s, \Omega}$}{Seminorm in $H^s(\Omega)$: $|u|_{s, \Omega} \coloneq \sum_{|\alpha|=s}\norm{\partial^\alpha u}{\Omega}$}
\nomenclature[D, 10]{$\norm{u}{s, \Omega}$}{Norm in $H^s(\Omega)$: $\norm{u}{s, \Omega} \coloneq \sum_{l \leq s} |u|_{l, \Omega}$}
% Molecular Quantum Mechanics
\nomenclature[E, 01]{$r, s, t$}{General \acrlong*{MO} indices}
\nomenclature[E, 02]{$i, j, k$}{Occupied \acrlong*{MO} indices}
\nomenclature[E, 03]{$a, b, c$}{Virtual \acrlong*{MO} indices}
\nomenclature[E, 04]{$\kappa, \lambda, \mu$}{One-electron basis functions indices}

### 2016-09-01 acronyms.tex
Update notations
Write some of the abstract
Massage the introduction
Save the day's work
Paper summaries done
Contributions chapter done
Work on CSM chapter
Switch to glossaries package for acronyms

\begin{acronym}
\acro{CC}{coupled cluster}
\acro{CCSD}{coupled cluster with single and double substitutions}
\acro{CI}{configuration interaction}
\acro{MO}{molecular orbital}
\acro{LR}{linear response}
\acro{DFT}{density-functional theory}
\acro{PCM}{polarizable continuum model}
\acro{MM}{molecular mechanics}
\acro{MP}{M{\o}ller--Plesset}
\acro{HF}{Hartree--Fock}
\acro{ASC}{apparent surface charge}
\acro{PTE}{perturbation to the energy}
\acro{PTED}{perturbation to the energy and the density}
\acro{QM/MM}{Quantum Mechanics/Molecular Mechanics}
\acro{DC}{Dielectric Continuum}
\acro{GEPOL}{GEPOL}
\acro{IEF}{Integral Equation Formalism}
\acro{LHS}{left-hand side}
\acro{MD}{Molecular Dynamics}
\acro{MM}{Molecular Mechanics}
\acro{BVP}{boundary value problem}
\acro{PDE}{partial differential equation}
\acro{PE}{Polarizable Embedding}
\acro{QC}{Quantum Chemistry}
\acro{RHS}{right-hand side}
\acro{SAS}{Solvent-Accessible Surface}
\acro{SES}{Solvent-Excluded Surface}
\acro{MEP}{molecular electrostatic potential}
\acro{TDSCF}{time-dependent SCF}
\acro{KS}{Kohn--Sham}
\end{acronym}

>>>>

\newacronym{API}{API}{application programming interface}
\newacronym{COSMO}{COSMO}{conductor-like screening model}
\newacronym{BO}{BO}{Born--Oppenheimer}
\newacronym[plural=PES, firstplural={potential energy surfaces (PESs)}]{PES}{PES}{potential energy surface}
\newacronym{CI}{CI}{configuration interaction}
\newacronym{CC}{CC}{coupled cluster}
\newacronym{CCS}{CCS}{coupled cluster with single substitutions}
\newacronym{CCSD}{CCSD}{coupled cluster with single and double substitutions}
\newacronym{CCSDT}{CCSDT}{coupled cluster with single, double and triple substitutions}
\newacronym{CC2}{CC2}{approximate coupled cluster singles and doubles}
\newacronym{CC3}{CC3}{approximate coupled cluster singles, doubles and triples}
\newacronym{PT}{PT}{perturbation theory}
\newacronym{MBPT}{MBPT}{many-body perturbation theory}
\newacronym{MO}{MO}{molecular orbital}
\newacronym{AO}{AO}{atomic orbital}
\newacronym{LR}{LR}{linear response}
\newacronym{DFT}{DFT}{density-functional theory}
\newacronym{PCM}{PCM}{polarizable continuum model}
\newacronym{MM}{MM}{molecular mechanics}
\newacronym{MP}{MP}{M{\o}ller--Plesset}
\newacronym{HF}{HF}{Hartree--Fock}
\newacronym{ASC}{ASC}{apparent surface charge}
\newacronym{PTE}{PTE}{perturbation-to-the-energy}
\newacronym{PTES}{PTES}{perturbation to the energy}
\newacronym{PTE(S)}{PTE(S)}{perturbation to the energy}
\newacronym{PTED}{PTED}{perturbation-to-the-energy-and-the-density}
\newacronym{IEF}{IEF}{integral equation formalism}
\newacronym{LHS}{LHS}{left-hand side}
\newacronym{MD}{MD}{molecular dynamics}
\newacronym{QM}{QM}{quantum mechanics}
\newacronym{BVP}{BVP}{boundary value problem}
\newacronym{BEM}{BEM}{boundary element method}
\newacronym{BIE}{BIE}{boundary integral equation}
\newacronym[plural=PDE, firstplural={partial differential equations (PDEs)}]{PDE}{PDE}{partial differential equation}
\newacronym{DtN}{DtN}{Dirichlet-to-Neumann}
\newacronym{PE}{PE}{polarizable embedding}
\newacronym{FQ}{FQ}{fluctuating charges}
\newacronym{QC}{QC}{quantum chemistry}
\newacronym{RHS}{RHS}{right-hand side}
\newacronym{vdWS}{vdWS}{van der Waals surface}
\newacronym{SAS}{SAS}{solvent-accessible surface}
\newacronym{SES}{SES}{solvent-excluded surface}
\newacronym{MEP}{MEP}{molecular electrostatic potential}
\newacronym{SCF}{SCF}{self-consistent field}
\newacronym{TDSCF}{TDSCF}{time-dependent SCF}
\newacronym{KS}{KS}{Kohn--Sham}
\newacronym{PWC}{PWC}{piecewise constant wavelet}
\newacronym{PWL}{PWL}{piecewise constant linear}
\newacronym{DC}{DC}{Dirac--Coulomb}
\newacronym{BCH}{BCH}{Baker--Campbell--Hausdorff}
\newacronym[plural=DVCS, firstplural={distributed version control systems (DVCSs)}]{DVCS}{DVCS}{distributed version control system}
\newacronym{EPR}{EPR}{electron paramagnetic resonance}
\newacronym{NMR}{NMR}{nuclear magnetic resonance}
\newacronym{pNMR}{pNMR}{paramagnetic nuclear magnetic resonance}
\newacronym{LGPL}{LGPL}{GNU Lesser General Public License}
\newacronym{AD}{AD}{automatic differentiation}
\newacronym{CSC}{CSC}{continuous surface charge}
\newacronym{SWIG}{SWIG}{switching/Gaussian}
